---
title: "Example: Using EIPIP Package"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../R/EIPIP.R")
library(caret)
library(MLmetrics)
library(mlbench) # To load the BreastCancer dataset
```

Firstly, we define a simple logistic regression as a base learner:

```{r base_learner}
# Define one or more of your base learner functions
learner <- function(df.train, metrics, OUTPUT, metric_optimize) {
    tC <- trainControl(
      summaryFunction = metrics,
      allowParallel = TRUE,
      classProbs = TRUE
    )
    
    rlog <- train(as.formula(sprintf("%s ~.", OUTPUT)),
      data = df.train,
      method = "glmnet",
      family = 'binomial',
      metric = metric_optimize,
      maximize = TRUE,
      trControl = tC
    )
    
    return(rlog)
}

```

Next, we load the BreastCancer data, and split it into a training set and a validation set:

```{r prepare_data}
# Load BreastCancer data
data(BreastCancer)
data <- BreastCancer
data <- data[, -c(1)]
data$Class <- factor(data$Class) # Making sure Class is a factor
data <- na.omit(data)
# Split into train and test set
indices <- createDataPartition(data$Class, p=0.8, list=FALSE)
train_set <- data[indices, ]
test_set <- data[-indices, ]

# Further split the train_set into train and validation set
indices <- createDataPartition(train_set$Class, p=0.8, list=FALSE)
val_set <- train_set[-indices,]
train_set <- train_set[indices, ]
```

Now we define the metric to be used and the metrics function.

```{r}
metrics <- function(data, lev = levels(as.factor(data$obs)), model = NULL){
    sensi = sensitivity(data[, "pred"],data[, "obs"],positive="malignant",negative="benign")

    met <- c(
    KAPPA = psych::cohen.kappa(cbind(data[, "obs"],data[, "pred"]))$kappa,
    SENS = sensi,
    BAL_ACC = ( sensi + specificity(data[, "pred"], data[, "obs"],positive="malignant",negative="benign"))/2
    )

  return(met)
}
```

Now we are ready to use the EIPIP class. We initialize an instance of the EIPIP class, train the model, and make predictions:

```{r eipip_example, warning=FALSE}
# Initialize EIPIP class
EIPIP_instance <- EIPIP$new(
  OUTPUT_VAR = "Class",
  OUTPUT_MIN = "malignant",
  OUTPUT_MAJ = "benign",
  conf = list(learner, learner, learner, learner, learner, learner, learner),
  metrics = metrics,
  TRAIN_METRIC = "BAL_ACC",
  exhaustive = FALSE
)

# Train the model
EIPIP_instance$train(train_set, val_set)

# Make predictions
predictions <- EIPIP_instance$predict(test_set)
```

Finally, we can evaluate the model performance over the stablished metrics in a test set.

```{r performance_evaluation}

EIPIP_instance$metricTest(test_set)
```
